\singlespacing \vspace{-1.5cm} \LARGE Trade-offs among plant floral and reproductive traits determine interactions with floral visitors

### 2021-08-13 Draft/Manuscript.Rmd
abbreviation of journal refs

Second, to better understand these complex trait relationships, we used regression trees. Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles. We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2). We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used _rpart.plot_ [@milborrow2015] version _3.0.9_ to plot the regression trees. We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors. We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits. We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig. S4).

>>>>

Second, to better understand these complex trait relationships, we used regression trees. Regression trees are recursive algorithms which can detect complex relationships among predictors and allow identification of the relevance of specific trait combinations on species functional roles. We focused exclusively on quantitative traits because almost all categorical traits were statistically associated with the first two axes of trait variation (Supplementary Table S2). We conducted this analysis using the _rpart_ package [@therneau2015] version _4.1-15_ with method _‘anova’_ with a minimum of 50 observations per terminal node and we used the _rpart.plot_ package [@milborrow2015] version _3.0.9_ to plot the regression trees. We considered the species level indices as response variables (interaction frequency, normalized degree and specialization) and we performed one regression tree per metric using the different quantitative traits as predictors. We calculated two regression trees per plant species-level metric, one for the full set of species and another for the subset of species for which we had pollen and nectar traits. We focused on regression trees that included floral rewards because they consistently showed pollen and nectar traits as being the best for explaining the different species-level metrics (see Supplementary Fig. S4).

### 2021-08-13 Draft/Manuscript.tex
abbreviation of journal refs

Second, to better understand these complex trait relationships, we used
regression trees. Regression trees are recursive algorithms which can
detect complex relationships among predictors and allow identification
of the relevance of specific trait combinations on species functional
roles. We focused exclusively on quantitative traits because almost all
categorical traits were statistically associated with the first two axes
of trait variation (Supplementary Table S2). We conducted this analysis
using the \emph{rpart}
package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}}
version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
observations per terminal node and we used
\emph{rpart.plot}\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
version \emph{3.0.9} to plot the regression trees. We considered the
species level indices as response variables (interaction frequency,
normalized degree and specialization) and we performed one regression
tree per metric using the different quantitative traits as predictors.
We calculated two regression trees per plant species-level metric, one
for the full set of species and another for the subset of species for
which we had pollen and nectar traits. We focused on regression trees
that included floral rewards because they consistently showed pollen and
nectar traits as being the best for explaining the different
species-level metrics (see Supplementary Fig. S4).

@@

\hypertarget{refs}{}
\hypertarget{ref-barrett2002}{}
1. Barrett, S. C. H. The evolution of plant sexual diversity.
\emph{Nature Reviews Genetics} \textbf{3}, 274--284 (2002).

\hypertarget{ref-schiestl2013}{}
2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of
floral signals. \emph{Trends in Ecology \& Evolution} \textbf{28},
307--315 (2013).

\hypertarget{ref-carvalheiro2014}{}
3. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
between co-flowering plants via shared pollinators depends on resource
abundance, accessibility and relatedness. \emph{Ecology Letters}
\textbf{17}, 1389--1399 (2014).

@@

\hypertarget{ref-moeller2017}{}
6. Moeller, D. A. \emph{et al.} Global biogeography of mating system
variation in seed plants. \emph{Ecology Letters} \textbf{20}, 375--384
(2017).

\hypertarget{ref-grossenbacher2017}{}
7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
over-represented on islands. \emph{New Phytologist} \textbf{215},
469--478 (2017).

@@

\hypertarget{ref-ruger2018}{}
9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
dimensions structuring a tropical tree community. \emph{Ecology Letters}
\textbf{21}, 1075--1084 (2018).

\hypertarget{ref-roddy2021}{}
10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
\emph{New Phytologist} \textbf{229}, 665--672 (2021).

@@

\hypertarget{ref-dellinger2020}{}
13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
we stand and where may we go? \emph{New Phytologist} \textbf{228},
1193--1213 (2020).

@@

\hypertarget{ref-chave2009}{}
21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
\emph{Ecology letters} \textbf{12}, 351--366 (2009).

@@

\hypertarget{ref-goodwillie2010}{}
24. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
and floral display traits in flowering plants and its implications for
the distribution of mating system variation. \emph{The New Phytologist}
\textbf{185}, 311--321 (2010).

@@

\hypertarget{ref-coux2016}{}
29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
species functional roles to their network roles. \emph{Ecology Letters}
\textbf{19}, 762--770 (2016).

@@

\hypertarget{ref-encinas2012}{}
41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
mutualistic network structure and diversity. \emph{Ecology letters}
\textbf{15}, 198--208 (2012).

@@

\hypertarget{ref-vazquez2005}{}
58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
as a surrogate for the total effect of animal mutualists on plants.
\emph{Ecology Letters} \textbf{8}, 1088--1094 (2005).

>>>>

Second, to better understand these complex trait relationships, we used
regression trees. Regression trees are recursive algorithms which can
detect complex relationships among predictors and allow identification
of the relevance of specific trait combinations on species functional
roles. We focused exclusively on quantitative traits because almost all
categorical traits were statistically associated with the first two axes
of trait variation (Supplementary Table S2). We conducted this analysis
using the \emph{rpart}
package\textsuperscript{\protect\hyperlink{ref-therneau2015}{65}}
version \emph{4.1-15} with method \emph{`anova'} with a minimum of 50
observations per terminal node and we used the \emph{rpart.plot}
package\textsuperscript{\protect\hyperlink{ref-milborrow2015}{66}}
version \emph{3.0.9} to plot the regression trees. We considered the
species level indices as response variables (interaction frequency,
normalized degree and specialization) and we performed one regression
tree per metric using the different quantitative traits as predictors.
We calculated two regression trees per plant species-level metric, one
for the full set of species and another for the subset of species for
which we had pollen and nectar traits. We focused on regression trees
that included floral rewards because they consistently showed pollen and
nectar traits as being the best for explaining the different
species-level metrics (see Supplementary Fig. S4).

@@

\hypertarget{refs}{}
\hypertarget{ref-barrett2002}{}
1. Barrett, S. C. H. The evolution of plant sexual diversity. \emph{Nat.
Rev. Genet.} \textbf{3}, 274--284 (2002).

\hypertarget{ref-schiestl2013}{}
2. Schiestl, F. P. \& Johnson, S. D. Pollinator-mediated evolution of
floral signals. \emph{Trends Ecol. Evol.} \textbf{28}, 307--315 (2013).

\hypertarget{ref-carvalheiro2014}{}
3. Carvalheiro, L. G. \emph{et al.} The potential for indirect effects
between co-flowering plants via shared pollinators depends on resource
abundance, accessibility and relatedness. \emph{Ecol. Lett.}
\textbf{17}, 1389--1399 (2014).

@@

\hypertarget{ref-moeller2017}{}
6. Moeller, D. A. \emph{et al.} Global biogeography of mating system
variation in seed plants. \emph{Ecol. Lett.} \textbf{20}, 375--384
(2017).

\hypertarget{ref-grossenbacher2017}{}
7. Grossenbacher, D. L. \emph{et al.} Self-compatibility is
over-represented on islands. \emph{New Phytol.} \textbf{215}, 469--478
(2017).

@@

\hypertarget{ref-ruger2018}{}
9. Rüger, N. \emph{et al.} Beyond the fastSlow continuum: Demographic
dimensions structuring a tropical tree community. \emph{Ecol. Lett.}
\textbf{21}, 1075--1084 (2018).

\hypertarget{ref-roddy2021}{}
10. Roddy, A. B. \emph{et al.} Towards the flower economics spectrum.
\emph{New Phytol.} \textbf{229}, 665--672 (2021).

@@

\hypertarget{ref-dellinger2020}{}
13. Dellinger, A. S. Pollination syndromes in the 21st century: Where do
we stand and where may we go? \emph{New Phytol.} \textbf{228},
1193--1213 (2020).

@@

\hypertarget{ref-chave2009}{}
21. Chave, J. \emph{et al.} Towards a worldwide wood economics spectrum.
\emph{Ecol. Lett.} \textbf{12}, 351--366 (2009).

@@

\hypertarget{ref-goodwillie2010}{}
24. Goodwillie, C. \emph{et al.} Correlated evolution of mating system
and floral display traits in flowering plants and its implications for
the distribution of mating system variation. \emph{New Phytol.}
\textbf{185}, 311--321 (2010).

@@

\hypertarget{ref-coux2016}{}
29. Coux, C., Rader, R., Bartomeus, I. \& Tylianakis, J. M. Linking
species functional roles to their network roles. \emph{Ecol. Lett.}
\textbf{19}, 762--770 (2016).

@@

\hypertarget{ref-encinas2012}{}
41. Encinas-Viso, F., Revilla, T. A. \& Etienne, R. S. Phenology drives
mutualistic network structure and diversity. \emph{Ecol. Lett.}
\textbf{15}, 198--208 (2012).

@@

\hypertarget{ref-vazquez2005}{}
58. Vázquez, D. P., Morris, W. F. \& Jordano, P. Interaction frequency
as a surrogate for the total effect of animal mutualists on plants.
\emph{Ecol. Lett.} \textbf{8}, 1088--1094 (2005).
